Figure 2 - Overview heatmaps for IP-MS and ChIP

### 2024-08-04 ms_figure_2_overview-heatmaps.Rmd
Some clean-up, Fig2 and Fig5

hm1a <- Heatmap(hmdata_150$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(hmdata_150$tstat, stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_150$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(
                    hmdata_150$tstat, complexes[complexLabel], 
                    idmap = idmap),
                bottom_annotation = makeColLabels(hmdata_150$tstat, colLabel_150, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hm2a <- Heatmap(hmdata_500$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(hmdata_500$tstat, stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_500$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(hmdata_500$tstat, complexes[complexLabel],
                                                         idmap = idmap, show_legend = FALSE),
                bottom_annotation = makeColLabels(hmdata_500$tstat, colLabel_500, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hmipmshot <- Heatmap(
    tstat, 
    col = circlize::colorRamp2(
        breaks = seq(3.0, 13.0, length.out = 64),
        colors = colorRampPalette(binary_heatmap_colors[c("FALSE", "TRUE")])(64)),
    border = TRUE,
    row_split = ifelse(rownames(tstat) %in% hot_tfs, "HOT TFs", "Other TFs"), 
    column_split = ifelse(colnames(tstat) %in% hot_tfs, "HOT TFs", "Other TFs"),
    cluster_rows = FALSE, cluster_columns = FALSE,
    row_title_gp = gpar(fontsize = fl), row_names_gp = gpar(fontsize = fs),
    column_title_gp = gpar(fontsize = fl), show_column_names = FALSE,
    heatmap_legend_param = list(labels_gp = gpar(fontsize = fs),
                                border = "gray10",
                                legend_direction = "horizontal",
                                legend_width = unit(24, "mm"),
                                title_position = "lefttop",
                                title_gp = gpar(fontsize = fl)),
    na_col = bg_color,
    name = "Mod. t-stat.")

@@

>>>>

hm1a <- Heatmap(hmdata_150$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_150$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(
                    hmdata_150$tstat, complexes[complexLabel], 
                    idmap = idmap),
                bottom_annotation = makeColLabels(hmdata_150$tstat, colLabel_150, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hm2a <- Heatmap(hmdata_500$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_500$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(hmdata_500$tstat, complexes[complexLabel],
                                                         idmap = idmap, show_legend = FALSE),
                bottom_annotation = makeColLabels(hmdata_500$tstat, colLabel_500, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hmipmshot <- Heatmap(
    tstat, 
    col = makeHeatmapCol(stringency = "high"), 
    border = TRUE,
    row_split = ifelse(rownames(tstat) %in% hot_tfs, "HOT TFs", "Other TFs"), 
    column_split = ifelse(colnames(tstat) %in% hot_tfs, "HOT TFs", "Other TFs"),
    cluster_rows = FALSE, cluster_columns = FALSE,
    row_title_gp = gpar(fontsize = fl), show_row_names = FALSE, 
    row_names_gp = gpar(fontsize = fs),
    column_title_gp = gpar(fontsize = fl), show_column_names = FALSE,
    heatmap_legend_param = list(labels_gp = gpar(fontsize = fs),
                                border = "gray10",
                                legend_direction = "horizontal",
                                legend_width = unit(24, "mm"),
                                title_position = "lefttop",
                                title_gp = gpar(fontsize = fl)),
    na_col = bg_color,
    name = "Mod. t-stat.")

@@

## Supplementary plots - PCA (IP-MS)

```{r}
## Low salt
sce150_pca <- einprot::doPCA(
    sce150[rowSums(!assay(sce150, 
                          metadata(sce150)$aNames$assayImputIndic)) >= 2, ],
    metadata(sce150)$aNames$assayImputed)$sce
df <- scuttle::makePerCellDF(sce150_pca, features = NULL, use.coldata = TRUE, 
                             use.dimred = TRUE) |>
    dplyr::mutate(Protocol = .capitalize(sub("_digest|_freeze", "", sub("SOP_", "", Protocol))))
pcvar150 <- attr(reducedDim(sce150_pca, paste0("PCA_", metadata(sce150)$aNames$assayImputed)), 
                 "percentVar")
(ggpca1 <- ggplot(
    df, 
    aes(x = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".1")]], 
        y = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".2")]], 
        color = Protocol)) + 
    geom_point(size = 3, alpha = 0.5) +
    scale_color_manual(values = c(Plate = main_colors[1], 
                                  Tube = main_colors[5]), name = "") + 
    coord_fixed() + 
    labs(x = paste0("PC1 (", round(pcvar150[1], 1), "%)"), 
         y = paste0("PC2 (", round(pcvar150[2], 1), "%)"), 
         title = "150 mM NaCl") + 
    theme_cowplot() + 
    theme(legend.position = "bottom") + 
    guides(color = guide_legend(nrow = 1, byrow = TRUE)))
(ggpca2 <- ggplot(
    df |>
        dplyr::mutate(bait = ifelse(Gene_name == "atf1", "Atf1", "Other baits")) |>
        dplyr::mutate(prot = .capitalize(prot)), 
    aes(x = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".1")]], 
        y = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".2")]], 
        color = bait, shape = prot)) + 
    geom_point(size = 3, alpha = 0.5) +
    scale_color_manual(values = c(Atf1 = main_colors[3], 
                                  `Other baits` = na_color), name = "") + 
    scale_shape_manual(values = c(Plate = 16, Tube = 17), name = "") + 
    coord_fixed() + 
    labs(x = paste0("PC1 (", round(pcvar150[1], 1), "%)"), 
         y = paste0("PC2 (", round(pcvar150[2], 1), "%)"), title = "150 mM NaCl") + 
    theme_cowplot() + 
    theme(legend.position = "bottom", legend.box = "vertical", 
          legend.box.just = "left", legend.margin = margin()))

sce500_pca <- einprot::doPCA(
    sce500[rowSums(!assay(sce500, metadata(sce500)$aNames$assayImputIndic)) >= 2, ],
    metadata(sce500)$aNames$assayImputed)$sce
df <- scuttle::makePerCellDF(sce500_pca, features = NULL, use.coldata = TRUE, 
                             use.dimred = TRUE)
pcvar500 <- attr(reducedDim(sce500_pca, paste0("PCA_", metadata(sce150)$aNames$assayImputed)), 
                 "percentVar")
(ggpca3 <- ggplot(
    df |>
        dplyr::mutate(bait = ifelse(Gene_name == "atf1", "Atf1", "Other baits")), 
    aes(x = .data[[paste0("PCA_", metadata(sce500)$aNames$assayImputed, ".1")]], 
        y = .data[[paste0("PCA_", metadata(sce500)$aNames$assayImputed, ".2")]], 
        color = bait)) + 
    geom_point(size = 3, alpha = 0.5) +
    scale_color_manual(values = c(Atf1 = main_colors[3], 
                                  `Other baits` = na_color), name = "") + 
    coord_fixed() + 
    labs(x = paste0("PC1 (", round(pcvar500[1], 1), "%)"), 
         y = paste0("PC2 (", round(pcvar500[2], 1), "%)"), 
         title = "500 mM NaCl") + 
    theme_cowplot() + 
    theme(legend.position = "bottom", legend.box.just = "left"))
```
